### 2021-01-31 docs/manuscript/PLOS-MSc-Thesis.tex
Improve introduction

Cells interact continuously with their environment and they must detect signals
from it. In many cases Gene Regulatory Networks (GRNs) interpret these signals
through gene interaction and produce a particular response. This information
processing function is of particular importance in developmental processes such
as those in which a group of cells differentiate in response to a signalling
molecule such as a morphogen \cite{Turing1952, Wolpert1969}. However, as
information processing by GRNs is often a complex process, one major goal of
developmental biology is to understand mechanistically how positional
information is translated in spatial differentiation.\\

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/GRN_660_topol_33_spatio-temp_exp_profile}
 \caption{\bf Most GRNs reach the steady state before 250 time steps.}
 GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
 expression profile (B).
 \label{fig:profile}
\end{figure}

@@

Although GRNs that produce a band of gene expression with only two nodes have
been described (e.g. the I-zero motif, \cite{Schaerli2014}) this is to our
knowledge the first time a GRN with a topology such as that of topology nine
and its expression mechanism are reported, increasing our knowledge of the
genotype-phenotype map in this kind of system.

However, it is still necessary to confirm experimentally the ability of this
topology to generate the described pattern and it would be interesting to
study its feasibility and possible implementation in synthetic gene regulatory
networks.

@@

>>>>

Cells interact continuously with their environment and they must detect signals
from it. In many cases Gene Regulatory Networks (GRNs) interpret these signals
through gene interaction and produce a particular response. This information
processing function is of particular importance in developmental processes such
as those in which a group of cells differentiate in response to a signalling
molecule. Such molecules were referred to as morphogens by Turing in 1952
\cite{Turing1952} and posterior theoretical studies on morphogens led to the
french flag model \cite{Wolpert1969}, in which a gradient of concentration of
the morphogen induces differentiation in a one-dimensional field of cells.
Although the Bicoid protein (bcd), the first example of a molecule that acted
as a morphogen, was only found in the 80's in the developing embryos of
\textit{Drosophila melanogaster}
\cite{driever_gradient_1988, driever_bicoid_1988}, now it is known that there
are many other examples such as the Decapentaplegic (Dpp) protein in
\textit{Drosophila} wing imaginal discs \cite{affolter_decapentaplegic_2007},
as well as Hedgehog and Wnt.
However, information processing by GRNs has proven to be a complex process, and
a major goal of developmental biology is to understand mechanistically how
positional information given by morphogens is translated in spatial
differentiation.\\

@@

@@

Although GRNs that produce a band of gene expression with only two nodes have
been described (e.g. the I-zero motif, \cite{Schaerli2014}) this is to our
knowledge the first time a GRN with a topology such as that of topology nine
(Fig \ref{fig:topol9})
and its expression mechanism are reported, increasing our knowledge of the
genotype-phenotype map in this kind of system, and it would be very interesting
to confirm experimentally the ability of this topology to generate the described
pattern and it would be interesting to study its feasibility and possible
implementation in synthetic gene regulatory networks.

@@

\paragraph*{S3 Fig.}
\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/supplementary-figures/GRN_660_topol_33_spatio-temp_exp_profile}
 \caption{\bf Most GRNs reach the steady state before 250 time steps.}
 GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
 expression profile (B).
 \label{S3_Fig}
\end{figure}
